---
title: "Chrysococcyx cupreus"
author: "Shelby M Palmer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### We first want to visualize where all recordings are coming from  
Read in XC and ML metadata containing lat/long  
Map points onto a projection of Africa  
```{r}
library(dplyr)
setwd("C:/Users/spalm/Desktop/C.cupreus")
xcmeta.cc <- read.csv("XC_metadata.csv")
mlmeta.cc <- read.csv("ML_metadata.csv")
usable.cc <- read.csv("usable_recordings.csv")

# rename ID column for ML recordings
colnames(mlmeta.cc)[which(colnames(mlmeta.cc)=="ML.Catalog.Number")] <- "Recording_ID"

# get a dataframe with lat/long and recording ID
latlong.cc <- rbind(xcmeta.cc[,which(colnames(xcmeta.cc)%in%c("Latitude", "Longitude", "Recording_ID"))],
                    mlmeta.cc[,which(colnames(mlmeta.cc)%in%c("Latitude", "Longitude", "Recording_ID"))])

# subset to only high-quality recordings and remove NAs
latlong.cc <- latlong.cc[which(latlong.cc$Recording_ID %in% usable.cc$Recording_ID),]
latlong.cc <- latlong.cc[-which(is.na(latlong.cc$Latitude)),]

### Make a map
library(ggplot2)
library(ggspatial)
library(sf)
# remotes::install_github("afrimapr/afrilearndata")
library(afrilearndata) # shapefiles for Africa

# Read in range map shapefile (downloaded from https://www.iucnredlist.org/resources/spatial-data-download)
cc_shape <- st_read(dsn = "./redlist_species_data_c-cupreus", layer = "data_0")

# Make the map
png("cc_map_range.png",
    width = 7,
    height = 7,
    units = "in",
    res = 600)
ggplot() +
  geom_sf(data = st_geometry(africountries)) +
  geom_sf(data = st_transform(cc_shape)[1,],
          color = "goldenrod3",
          fill = "goldenrod3",
          alpha = 0.5) +
  geom_sf(data = st_transform(cc_shape)[2,],
          color = "indianred",
          fill = "indianred",
          alpha = 0.5) +
  geom_point(data = latlong.cc, 
             aes(x = Longitude, 
                 y = Latitude),
             size = 1.5,
             color = "black",
             alpha = 0.5,
             shape = 19) +
  coord_sf(xlim = c(-20, 52),
           ylim = c(-35, 20)) +
  theme_bw()
dev.off()


```

### Testing threshold-based frequency measurements
```{r}
library(seewave)
library(tuneR)
library(dplyr)
cleancc <- readWave(paste(getwd(), 
                          "/practice_recordings/8596_23.94.wav", 
                          sep = "")) %>%
  fir(., from = 1000, to = 6000, bandpass = T, output = "Wave")
noisycc <- readWave(paste(getwd(), 
                          "/practice_recordings/8597_41.28.wav", 
                          sep = "")) %>%
  fir(., from = 1000, to = 6000, bandpass = T, output = "Wave")
## Clean
# timer objects
cleannotes <- timer(cleancc, dmin = 0.05, threshold = 12, msmooth = c(512, 90))
cleancc_1 <- cutw(cleancc, from = cleannotes$s.start[1], to = cleannotes$s.end[1], output = "Wave")
# compute and visualize frequency spectrum
spec(cleancc_1, flim = c(0, 5), alim = c(-40, 0), wl = 1024, ovlp = 95, dB = "max0")
abline(h = -15, lty = 2)
spectro(cleancc, flim = c(0,6), tlim = c(0,2), wl = 1024, ovlp = 95)
# get min and max values
crit <- -15 # WARNING: arbitrary value
maxfreq <- max(meanspec(cleancc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][meanspec(cleancc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
maxfreq

minfreq <- min(spec(cleancc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][spec(cleancc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
minfreq

## Noisy
# timer objects
noisynotes <- timer(noisycc, dmin = 0.05, threshold = 12, msmooth = c(512, 90))
noisycc_1 <- cutw(noisycc, from = noisynotes$s.start[1], to = noisynotes$s.end[1], output = "Wave")
# compute and visualize frequency spectrum
spec(noisycc_1, flim = c(0, 5), alim = c(-40, 0), wl = 1024, ovlp = 95, dB = "max0")
abline(h = -15, lty = 2)
spectro(noisycc, flim = c(0,6), tlim = c(0,2), wl = 1024, ovlp = 95)
# get min and max
maxfreq <- max(meanspec(noisycc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][meanspec(noisycc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
maxfreq

minfreq <- min(meanspec(noisycc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][spec(noisycc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
minfreq

## Try putting it in a function

```

### Functions to automate acoustic measurements at the note level  
`x` is a wave file  
`y` is a `timer()` object  
`t` is the total number of element divisions (set `t = 1` for whole-element measurements)  
`n` is the element division # for which this measurement is desired
```{r}
# get an example recording
library(tuneR)
library(seewave)
ccex <- readWave(paste(getwd(),
                       "/sims_test/Chrysococcyx-cupreus-615909_0.04.wav",
                       sep = ""))
ccex.s <- timer(ccex, threshold = 12, msmooth = c(256, 95), dmin = 0.01)
duration(ccex)
ccex.1 <- cutw(ccex, from = ccex.s$s.start[1], to = ccex.s$s.start[1]+((1/4)*ccex.s$s[1]),
               output = "Wave")
duration(ccex.1)
meanspec(ccex.1,
         flim=c(1, 10), 
         wl = 540,
         ovlp = 95,
         dB='max0',
         plot = F)

crit = -20 # chosen critical value
# maximum frequency
CCMaxFreq <- function(x, y, t, n) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- max(meanspec(x,
                         from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                         to = y$s.start[j]+(y$s[j]*(n/t)), 
                         flim=c(1, 6), 
                         wl = 512,
                         ovlp = 95,
                         dB='max0',
                         plot = F)[,1][meanspec(x,
                                                from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                                to = y$s.start[j]+(y$s[j]*(n/t)), 
                                                flim=c(1, 6), 
                                                wl = 512,
                                                ovlp = 95, 
                                                dB='max0',
                                                plot = F)[,2]>crit])
  }
  return(z)
}


# minimum frequency
CCMinFreq <- function(x,y,n,t) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- min(meanspec(x,
                         from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                         to = y$s.start[j]+(y$s[j]*(n/t)), 
                         flim=c(1, 6), 
                         wl = 512,
                         ovlp = 95,
                         dB='max0',
                         plot = F)[,1][meanspec(x,
                                                from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                                to = y$s.start[j]+(y$s[j]*(n/t)), 
                                                flim=c(1, 6), 
                                                wl = 512,
                                                ovlp = 95, 
                                                dB='max0',
                                                plot = F)[,2]>crit])
  }
  return(z)
}

# peak frequency
CCPeakFreq <- function(x,y,n,t) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- meanspec(x,
                     from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                     to = y$s.start[j]+(y$s[j]*(n/t)), 
                     flim=c(1, 6), 
                     wl = 512,
                     ovlp = 95,
                     dB='max0',
                     plot = F)[,1][match(c(0),
                                          meanspec(x,
                                          from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                          to = y$s.start[j]+(y$s[j]*(n/t)), 
                                     flim=c(1, 6), 
                                     wl = 512,
                                     ovlp = 95,
                                     dB='max0',
                                     plot = F)[,2])]
  }
  return(z)
}

# Maximum dominant frequency slope
CCDomFreqMaxSlope <- function(x,y,n,t) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- max(diff(dfreq(x,
                          tlim = c(y$s.start[j]+(y$s[j]*((n-1)/t)), 
                                   y$s.start[j]+(y$s[j]*(n/t))),
                          ovlp = 95,
                          wl = 512,
                          threshold = 5,
                          plot = F)[,2]))
  }
  return(z)
}

CCDomFreqMaxSlope(ccex, ccex.s, n=1, t=4)


# Minimum dominant frequency slope
CCDomFreqMinSlope <- function(x,y,n,t) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- min(diff(dfreq(x,
                          tlim = c(y$s.start[j]+(y$s[j]*((n-1)/t)), 
                                   y$s.start[j]+(y$s[j]*(n/t))),
                          ovlp = 95,
                          wl = 512,
                          threshold = 5,
                          plot = F)[,2]))
  }
  return(z)
}

CCEntropy <- function(x,y) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- sh(
      meanspec(x,
               from = y$s.start[j],
               to = y$s.end[j], 
               flim=c(1, 6), 
               wl = 512,
               ovlp = 95,
               plot = F
      )
    )
  }
  return(z)
}

CCEntropy(x = ccex, y = ccex.s)

diff(dfreq(ccex,
                          tlim = c(ccex.s$s.start[4]+(ccex.s$s[4]*((4-1)/4)), 
                                   ccex.s$s.start[4]+(ccex.s$s[4]*(4/4))),
                          ovlp = 95,
                          wl = 512,
                          threshold = 2,
                          plot = F)[,2])

spectro(ccex)

```
  
## Simulations  
### Make a dataframe with measurements from each song in a single high-quality recording  
```{r}
simsdf <- read.csv("sims_df.csv")
colnames(simsdf)

simswd <- paste(getwd(),
      "/sims_test/",
      sep = "")

for (i in 1:length(list.files(simswd))) {
  simsdf$ID[i] <- list.files(simswd)[i]
  a <- readWave(paste(simswd, list.files(simswd)[i], sep = ""))
  b <- timer(a, threshold = 12, msmooth = c(256, 95), dmin = 0.01)
  simsdf$n1_s1_pk[i] <- CCPeakFreq(a, b, n = 1, t = 4)[1]
  simsdf$n1_s2_pk[i] <- CCPeakFreq(a, b, n = 2, t = 4)[1]
  simsdf$n1_s3_pk[i] <- CCPeakFreq(a, b, n = 3, t = 4)[1]
  simsdf$n1_s4_pk[i] <- CCPeakFreq(a, b, n = 4, t = 4)[1]
  simsdf$n2_s1_pk[i] <- CCPeakFreq(a, b, n = 1, t = 4)[2]
  simsdf$n2_s2_pk[i] <- CCPeakFreq(a, b, n = 2, t = 4)[2]
  simsdf$n2_s3_pk[i] <- CCPeakFreq(a, b, n = 3, t = 4)[2]
  simsdf$n2_s4_pk[i] <- CCPeakFreq(a, b, n = 4, t = 4)[2]
  simsdf$n3_s1_pk[i] <- CCPeakFreq(a, b, n = 1, t = 4)[3]
  simsdf$n3_s2_pk[i] <- CCPeakFreq(a, b, n = 2, t = 4)[3]
  simsdf$n3_s3_pk[i] <- CCPeakFreq(a, b, n = 3, t = 4)[3]
  simsdf$n3_s4_pk[i] <- CCPeakFreq(a, b, n = 4, t = 4)[3]
  simsdf$n4_s1_pk[i] <- CCPeakFreq(a, b, n = 1, t = 4)[4]
  simsdf$n4_s2_pk[i] <- CCPeakFreq(a, b, n = 2, t = 4)[4]
  simsdf$n4_s3_pk[i] <- CCPeakFreq(a, b, n = 3, t = 4)[4]
  simsdf$n4_s4_pk[i] <- CCPeakFreq(a, b, n = 4, t = 4)[4]
  
  simsdf$n1_s1_max[i] <- CCMaxFreq(a, b, n = 1, t = 4)[1]
  simsdf$n1_s2_max[i] <- CCMaxFreq(a, b, n = 2, t = 4)[1]
  simsdf$n1_s3_max[i] <- CCMaxFreq(a, b, n = 3, t = 4)[1]
  simsdf$n1_s4_max[i] <- CCMaxFreq(a, b, n = 4, t = 4)[1]
  simsdf$n2_s1_max[i] <- CCMaxFreq(a, b, n = 1, t = 4)[2]
  simsdf$n2_s2_max[i] <- CCMaxFreq(a, b, n = 2, t = 4)[2]
  simsdf$n2_s3_max[i] <- CCMaxFreq(a, b, n = 3, t = 4)[2]
  simsdf$n2_s4_max[i] <- CCMaxFreq(a, b, n = 4, t = 4)[2]
  simsdf$n3_s1_max[i] <- CCMaxFreq(a, b, n = 1, t = 4)[3]
  simsdf$n3_s2_max[i] <- CCMaxFreq(a, b, n = 2, t = 4)[3]
  simsdf$n3_s3_max[i] <- CCMaxFreq(a, b, n = 3, t = 4)[3]
  simsdf$n3_s4_max[i] <- CCMaxFreq(a, b, n = 4, t = 4)[3]
  simsdf$n4_s1_max[i] <- CCMaxFreq(a, b, n = 1, t = 4)[4]
  simsdf$n4_s2_max[i] <- CCMaxFreq(a, b, n = 2, t = 4)[4]
  simsdf$n4_s3_max[i] <- CCMaxFreq(a, b, n = 3, t = 4)[4]
  simsdf$n4_s4_max[i] <- CCMaxFreq(a, b, n = 4, t = 4)[4]
  
  simsdf$n1_s1_min[i] <- CCMinFreq(a, b, n = 1, t = 4)[1]
  simsdf$n1_s2_min[i] <- CCMinFreq(a, b, n = 2, t = 4)[1]
  simsdf$n1_s3_min[i] <- CCMinFreq(a, b, n = 3, t = 4)[1]
  simsdf$n1_s4_min[i] <- CCMinFreq(a, b, n = 4, t = 4)[1]
  simsdf$n2_s1_min[i] <- CCMinFreq(a, b, n = 1, t = 4)[2]
  simsdf$n2_s2_min[i] <- CCMinFreq(a, b, n = 2, t = 4)[2]
  simsdf$n2_s3_min[i] <- CCMinFreq(a, b, n = 3, t = 4)[2]
  simsdf$n2_s4_min[i] <- CCMinFreq(a, b, n = 4, t = 4)[2]
  simsdf$n3_s1_min[i] <- CCMinFreq(a, b, n = 1, t = 4)[3]
  simsdf$n3_s2_min[i] <- CCMinFreq(a, b, n = 2, t = 4)[3]
  simsdf$n3_s3_min[i] <- CCMinFreq(a, b, n = 3, t = 4)[3]
  simsdf$n3_s4_min[i] <- CCMinFreq(a, b, n = 4, t = 4)[3]
  simsdf$n4_s1_min[i] <- CCMinFreq(a, b, n = 1, t = 4)[4]
  simsdf$n4_s2_min[i] <- CCMinFreq(a, b, n = 2, t = 4)[4]
  simsdf$n4_s3_min[i] <- CCMinFreq(a, b, n = 3, t = 4)[4]
  simsdf$n4_s4_min[i] <- CCMinFreq(a, b, n = 4, t = 4)[4]
  
  simsdf$n1_s1_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 1, t = 4)[1]
  simsdf$n1_s2_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 2, t = 4)[1]
  simsdf$n1_s3_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 3, t = 4)[1]
  simsdf$n1_s4_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 4, t = 4)[1]
  simsdf$n2_s1_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 1, t = 4)[2]
  simsdf$n2_s2_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 2, t = 4)[2]
  simsdf$n2_s3_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 3, t = 4)[2]
  simsdf$n2_s4_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 4, t = 4)[2]
  simsdf$n3_s1_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 1, t = 4)[3]
  simsdf$n3_s2_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 2, t = 4)[3]
  simsdf$n3_s3_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 3, t = 4)[3]
  simsdf$n3_s4_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 4, t = 4)[3]
  simsdf$n4_s1_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 1, t = 4)[4]
  simsdf$n4_s2_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 2, t = 4)[4]
  simsdf$n4_s3_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 3, t = 4)[4]
  simsdf$n4_s4_maxsl[i] <- CCDomFreqMaxSlope(a, b, n = 4, t = 4)[4]
  
  simsdf$n1_s1_minsl[i] <- CCDomFreqMinSlope(a, b, n = 1, t = 4)[1]
  simsdf$n1_s2_minsl[i] <- CCDomFreqMinSlope(a, b, n = 2, t = 4)[1]
  simsdf$n1_s3_minsl[i] <- CCDomFreqMinSlope(a, b, n = 3, t = 4)[1]
  simsdf$n1_s4_minsl[i] <- CCDomFreqMinSlope(a, b, n = 4, t = 4)[1]
  simsdf$n2_s1_minsl[i] <- CCDomFreqMinSlope(a, b, n = 1, t = 4)[2]
  simsdf$n2_s2_minsl[i] <- CCDomFreqMinSlope(a, b, n = 2, t = 4)[2]
  simsdf$n2_s3_minsl[i] <- CCDomFreqMinSlope(a, b, n = 3, t = 4)[2]
  simsdf$n2_s4_minsl[i] <- CCDomFreqMinSlope(a, b, n = 4, t = 4)[2]
  simsdf$n3_s1_minsl[i] <- CCDomFreqMinSlope(a, b, n = 1, t = 4)[3]
  simsdf$n3_s2_minsl[i] <- CCDomFreqMinSlope(a, b, n = 2, t = 4)[3]
  simsdf$n3_s3_minsl[i] <- CCDomFreqMinSlope(a, b, n = 3, t = 4)[3]
  simsdf$n3_s4_minsl[i] <- CCDomFreqMinSlope(a, b, n = 4, t = 4)[3]
  simsdf$n4_s1_minsl[i] <- CCDomFreqMinSlope(a, b, n = 1, t = 4)[4]
  simsdf$n4_s2_minsl[i] <- CCDomFreqMinSlope(a, b, n = 2, t = 4)[4]
  simsdf$n4_s3_minsl[i] <- CCDomFreqMinSlope(a, b, n = 3, t = 4)[4]
  simsdf$n4_s4_minsl[i] <- CCDomFreqMinSlope(a, b, n = 4, t = 4)[4]
  
  simsdf$n1_entr[i] <- CCEntropy(a, b)[1]
  simsdf$n2_entr[i] <- CCEntropy(a, b)[2]
  simsdf$n3_entr[i] <- CCEntropy(a, b)[3]
  simsdf$n4_entr[i] <- CCEntropy(a, b)[4]
  
  simsdf$n1_dur[i] <- b$s[1]
  simsdf$n2_dur[i] <- b$s[2]
  simsdf$n3_dur[i] <- b$s[3]
  simsdf$n4_dur[i] <- b$s[4]
}

# these are measurements for each variable across the songs in a single recording. the purpose of this dataframe is to provide a basis (central tendencies and variance) for data simulation.
write.csv(simsdf, "simsdf_full.csv", row.names = F)

# Number of recordings in the dataset
# N <- 100

# probability of sampling each 
# songs_probs <- c(0.013157895, 0.16447368, 0.16447368, 0.01316, 0.4310526,
#            0.021381579, 0.011513158, 0.008223684, 0.009868421, 0.006578947,
#            0.004934211, 0.006578947, 0.001644737, 0.001644737, 0.001644737,
#            0.001644737, 0.001644737)
# 
# n_songs <- c(1:12,14,15,18,20,29) # number of songs recorded per bird in our dataset
# 
# sim_nrec <- sample(n_songs, size=100, replace=TRUE, prob=songs_probs)
#
#

# Read in data
read.csv("C:/Users/spalm/Desktop/C.cupreus/simsdf_full.csv")
# unique numbers of songs produced
n_songs <- c(1:12,14,15,18,22,29)
# number of recordings for which the corresponding n_songs is true
number_of_samp_size_occurrence <- c(8,9,10,7,17,12,7,6,6,4,3,3,1,1,1,1,1)

# make a vector whose length = total number of recordings and whose content reflects number of songs per recording (sum of nrec = total number of songs in dataset)
nrec <- rep(n_songs[1], number_of_samp_size_occurrence[1])
for (i in 2:length(n_songs)) {
  nrec <- c(nrec, 
            rep(n_songs[i], number_of_samp_size_occurrence[i])
            )
}


# Make a vector of names of individuals to be simulated
names <- rep(paste("ind", 1, sep = "_"), 
    length = nrec[1])
for(i in 2:length(nrec)) {
  names <- c(names, rep(paste("ind", i, sep = "_"), 
                          length = nrec[i]))
}

names

# We need to simulate each measurement with means based on the real measurements from `simsdf`
i <- 1 # first individual
j <- 2 # second column, first measurement (first column is IDs)
rnorm(n=nrec[i], 
      mean=rnorm(n = 1,
                 mean=mean(simsdf[,j]), 
                 sd=sd(simsdf[,j])), # add noise to the individual mean that's sampled
      sd=sd(simsdf[,j])/5) # add less noise between an individual's songs

# The standard deviation values taken from `simsdf` can (should?) be replaced by constants


#####

# establish a dataframe where we'll put the simulated measurements
actualsims <- as.data.frame(
  matrix(data = NA,
                     nrow = sum(nrec),
                     ncol = length(colnames(simsdf)))
  )

# give the columns names according to `simsdf`
colnames(actualsims) <- colnames(simsdf)

# add simulated individual names to the ID column
actualsims$ID <- names


# loop
# sorry for using h
# we start at 2 because the first column is just ID's
for (h in 2:length(colnames(actualsims))) {
  # simulate measurements of the hth column for only the first value of `nrec`
  varh <- rnorm(n=nrec[1], 
                mean=rnorm(n = 1,
                          mean=mean(simsdf[,h]), 
                          sd=sd(simsdf[,h])),
                sd=sd(simsdf[,h])/5)
  # fill in with the rest of the values indicated by `nrec`
  for(i in 2:length(nrec)) {
    varh <- c(varh, rep(
      rnorm(n=nrec[i], 
            mean=rnorm(n = 1,
                      mean=mean(simsdf[,h]), 
                      sd=sd(simsdf[,h])),
            sd=sd(simsdf[,h])/5),
      length = nrec[i]
      )
    )
  }
  # add the concatenated values to the hth column
  actualsims[,h] <- varh
}

# write out a .csv file
write.csv(actualsims, "cuckoo_data_sims.csv", row.names = F)





```



## A figure displaying an African Emerald Cuckoo song with each frequency measurement displayed  
```{r}
# get an example recording
library(tuneR)
library(seewave)
ccex <- readWave(paste(getwd(),
                       "/sims_test/Chrysococcyx-cupreus-615909_0.04.wav",
                       sep = ""))
# make timer object
ccex.s <- timer(ccex, threshold = 12, msmooth = c(256, 95), dmin = 0.01)
# set a critical value (dB below max amplitude)
crit <- -20
#
# make spectrogram with slice frequency measurements overlaid
spectro(ccex, 
        scale = F, grid = F, 
        flim = c(0,6),
        tlim = c(0.4, duration(ccex)),
        collevels = seq(-30, 0, by = 0.1),
        ovlp = 95,
        palette = reverse.gray.colors.2);
for (i in 1:length(ccex.s$s)) {
  for (j in 1:4) {
      segments(y0 = CCMaxFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        y1 = CCMaxFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        x0 = ccex.s$s.start[i]+(ccex.s$s[i]*((j-1)/4)), 
        x1 = ccex.s$s.start[i]+(ccex.s$s[i]*(j/4)),
        col = "red"
        )
      segments(y0 = CCMinFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        y1 = CCMinFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        x0 = ccex.s$s.start[i]+(ccex.s$s[i]*((j-1)/4)), 
        x1 = ccex.s$s.start[i]+(ccex.s$s[i]*(j/4)),
        col = "green"
        )
      segments(y0 = CCPeakFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        y1 = CCPeakFreq(x = ccex, y = ccex.s, n = j, t = 4)[i],
        x0 = ccex.s$s.start[i]+(ccex.s$s[i]*((j-1)/4)), 
        x1 = ccex.s$s.start[i]+(ccex.s$s[i]*(j/4)),
        col = "cyan"
        )
      segments(y0 = 1, y1 = 5,
        x0 = ccex.s$s.start[i]+(ccex.s$s[i]*((j-1)/4)),
        x1 = ccex.s$s.start[i]+(ccex.s$s[i]*((j-1)/4))
        )
  }
  segments(y0 = 1, y1 = 5,
           x0 = ccex.s$s.end[i],
           x1 = ccex.s$s.end[i]
  )
  
}


library(tuneR)
a <- readWave(paste(getwd(), "/chopped_recordings/8596_23.94.wav", sep = ""))

a@samp.rate

originalwd <- paste(getwd(), "/chopped_recordings/", sep = "")
sampratesdf <- data.frame(file = list.files(originalwd),
                          samprates = rep(NA))

for (i in 1:length(list.files(originalwd))) {
  a <- readWave(paste(originalwd, list.files(originalwd)[i], sep = ""))
  sampratesdf$samprates[i] <- a@samp.rate
}
#
table(sampratesdf$samprates)

sampratesdf[which(sampratesdf$samprates<40000),]

```
  
### 20 September 2024: Filter and resample again  
To fix the issue of frequency spectrum calculation limitation by sampling frequency, we will double the standard sampling rate (to 44100 Hz)  
```{r}
library(dplyr)
# loop through `chopped_recordings`, deposit new files in `filter_resamp_44100`
for (i in 1:length(list.files(originalwd))) {

  a <- readWave(
        paste(originalwd, 
              list.files(originalwd)[i],
              sep = "")
      ) %>%
    fir(., from = 1000, to = 5100, output = "Wave") %>%
    normalize(., unit = "16")
  
  if (a@samp.rate!=44100) {
      a <- resamp(a, g = 44100, output = "Wave")
  }
  
  writeWave(a, filename = paste(getwd(), "/filter_resamp_44100/",
                                list.files(originalwd)[i],
                                sep = ""))
  
}



```
How will we collapse individual-level duplicates?
```{r}

```

