---
title: "Chrysococcyx cupreus"
author: "Shelby M Palmer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### We first want to visualize where all recordings are coming from  
Read in XC and ML metadata containing lat/long  
Map points onto a projection of Africa  
```{r}
library(dplyr)
setwd("C:/Users/spalm/Desktop/C.cupreus")
xcmeta.cc <- read.csv("XC_metadata.csv")
mlmeta.cc <- read.csv("ML_metadata.csv")
usable.cc <- read.csv("usable_recordings.csv")

# rename ID column for ML recordings
colnames(mlmeta.cc)[which(colnames(mlmeta.cc)=="ML.Catalog.Number")] <- "Recording_ID"

# get a dataframe with lat/long and recording ID
latlong.cc <- rbind(xcmeta.cc[,which(colnames(xcmeta.cc)%in%c("Latitude", "Longitude", "Recording_ID"))],
                    mlmeta.cc[,which(colnames(mlmeta.cc)%in%c("Latitude", "Longitude", "Recording_ID"))])

# subset to only high-quality recordings and remove NAs
latlong.cc <- latlong.cc[which(latlong.cc$Recording_ID %in% usable.cc$Recording_ID),]
latlong.cc <- latlong.cc[-which(is.na(latlong.cc$Latitude)),]

### Make a map
library(ggplot2)
library(ggspatial)
library(sf)
# remotes::install_github("afrimapr/afrilearndata")
library(afrilearndata) # shapefiles for Africa

# Read in range map shapefile (downloaded from https://www.iucnredlist.org/resources/spatial-data-download)
cc_shape <- st_read(dsn = "./redlist_species_data_c-cupreus", layer = "data_0")

# Make the map
png("cc_map_range.png",
    width = 7,
    height = 7,
    units = "in",
    res = 600)
ggplot() +
  geom_sf(data = st_geometry(africountries)) +
  geom_sf(data = st_transform(cc_shape)[1,],
          color = "goldenrod3",
          fill = "goldenrod3",
          alpha = 0.5) +
  geom_sf(data = st_transform(cc_shape)[2,],
          color = "indianred",
          fill = "indianred",
          alpha = 0.5) +
  geom_point(data = latlong.cc, 
             aes(x = Longitude, 
                 y = Latitude),
             size = 1.5,
             color = "black",
             alpha = 0.5,
             shape = 19) +
  coord_sf(xlim = c(-20, 52),
           ylim = c(-35, 20)) +
  theme_bw()
dev.off()


```

### Testing threshold-based frequency measurements
```{r}
library(seewave)
library(tuneR)
library(dplyr)
cleancc <- readWave(paste(getwd(), 
                          "/practice_recordings/8596_23.94.wav", 
                          sep = "")) %>%
  fir(., from = 1000, to = 6000, bandpass = T, output = "Wave")
noisycc <- readWave(paste(getwd(), 
                          "/practice_recordings/8597_41.28.wav", 
                          sep = "")) %>%
  fir(., from = 1000, to = 6000, bandpass = T, output = "Wave")
## Clean
# timer objects
cleannotes <- timer(cleancc, dmin = 0.05, threshold = 12, msmooth = c(512, 90))
cleancc_1 <- cutw(cleancc, from = cleannotes$s.start[1], to = cleannotes$s.end[1], output = "Wave")
# compute and visualize frequency spectrum
spec(cleancc_1, flim = c(0, 5), alim = c(-40, 0), wl = 1024, ovlp = 95, dB = "max0")
abline(h = -15, lty = 2)
spectro(cleancc, flim = c(0,6), tlim = c(0,2), wl = 1024, ovlp = 95)
# get min and max values
crit <- -15 # WARNING: arbitrary value
maxfreq <- max(meanspec(cleancc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][meanspec(cleancc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
maxfreq

minfreq <- min(spec(cleancc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][spec(cleancc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
minfreq

## Noisy
# timer objects
noisynotes <- timer(noisycc, dmin = 0.05, threshold = 12, msmooth = c(512, 90))
noisycc_1 <- cutw(noisycc, from = noisynotes$s.start[1], to = noisynotes$s.end[1], output = "Wave")
# compute and visualize frequency spectrum
spec(noisycc_1, flim = c(0, 5), alim = c(-40, 0), wl = 1024, ovlp = 95, dB = "max0")
abline(h = -15, lty = 2)
spectro(noisycc, flim = c(0,6), tlim = c(0,2), wl = 1024, ovlp = 95)
# get min and max
maxfreq <- max(meanspec(noisycc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][meanspec(noisycc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
maxfreq

minfreq <- min(meanspec(noisycc_1, 
                        flim=c(0,6), 
                        wl = 1024, 
                        dB = "max0",
                        plot=F)[,1][spec(noisycc_1, 
                                                flim=c(0,6), 
                                                wl = 1024, 
                                                dB="max0",
                                             plot=F)[,2]>crit])
minfreq

## Try putting it in a function

```

### Functions to automate acoustic measurements at the note level  
`x` is a wave file  
`y` is a `timer()` object  
`t` is the total number of element divisions (set `t = 1` for whole-element measurements)  
`n` is the element division # for which this measurement is desired
```{r}
# get an example recording
ccex <- readWave(paste(getwd(),
                       "/filter_resamp/filtered_Chrysococcyx-cupreus-780410_1.29.wav",
                       sep = ""))
ccex.s <- timer(ccex, threshold = 12, msmooth = c(256, 95), dmin = 0.01)
ccex.1 <- cutw(ccex, from = ccex.s$s.start[1], to = ccex.s$s.start[1]+(0.25*ccex.s$s[1]),
               output = "Wave")
duration(ccex.1)
meanspec(ccex.1,
         flim=c(1, 10), 
         wl = 512,
         ovlp = 75,
         dB='max0',
         plot = F)

crit = -20 # chosen critical value
# maximum frequency
CCMaxFreq <- function(x, y, t, n) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- max(meanspec(x,
                         from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                         to = y$s.start[j]+(y$s[j]*(n/t)), 
                         flim=c(1, 6), 
                         wl = 512,
                         ovlp = 75,
                         dB='max0',
                         plot = F)[,1][meanspec(x,
                                                from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                                to = y$s.start[j]+(y$s[j]*(n/t)), 
                                                flim=c(1, 6), 
                                                wl = 512,
                                                ovlp = 75, 
                                                dB='max0',
                                                plot = F)[,2]>crit])
  }
  return(z)
}

CCMaxFreq(x=ccex, y=ccex.s, t=4, n=1)

# minimum frequency
CCMinFreq <- function(x,y,n,t) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- min(meanspec(x,
                         from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                         to = y$s.start[j]+(y$s[j]*(n/t)), 
                         flim=c(1, 6), 
                         wl = 512,
                         ovlp = 75,
                         dB='max0',
                         plot = F)[,1][meanspec(x,
                                                from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                                to = y$s.start[j]+(y$s[j]*(n/t)), 
                                                flim=c(1, 6), 
                                                wl = 512,
                                                ovlp = 75, 
                                                dB='max0',
                                                plot = F)[,2]>crit])
  }
  return(z)
}

# peak frequency
CCPeakFreq <- function(x,y) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- meanspec(x,
                     from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                     to = y$s.start[j]+(y$s[j]*(n/t)), 
                     flim=c(1, 6), 
                     wl = 512,
                     ovlp = 75,
                     dB='max0',
                     plot = F)[,1][match(c(0),
                                          meanspec(x,
                                          from = y$s.start[j]+(y$s[j]*((n-1)/t)),
                                          to = y$s.start[j]+(y$s[j]*(n/t)), 
                                     flim=c(1, 6), 
                                     wl = 512,
                                     ovlp = 75,
                                     dB='max0',
                                     plot = F)[,2])]
  }
  return(z)
}

# Maximum dominant frequency slope
CCDomFreqMaxSlope <- function(x,y) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- max(diff(dfreq(x,
                          tlim = c(y$s.start[j], y$s.end[j]),
                          ovlp = 75,
                          wl = 512,
                          threshold = 5,
                          plot = F)[,2]))
  }
  return(z)
}


# Minimum dominant frequency slope
CCDomFreqMinSlope <- function(x,y) {
  z <- c()
  for (j in 1:length(y$s.start)) {
    z[j] <- min(diff(dfreq(x,
                          tlim = c(y$s.start[j], y$s.end[j]),
                          ovlp = 95,
                          wl = 1024,
                          threshold = 5,
                          plot = F)[,2]))
  }
  return(z)
}

```

## A figure displaying an African Emerald Cuckoo song with each frequency measurement displayed  
```{r}
ccex <- readWave(paste(getwd(),
                       "/filter_resamp/filtered_23167_26.00.wav",
                       sep = ""))
ccex.s <- timer(ccex, threshold = 12, msmooth = c(512, 95), dmin = 0.01)

crit <- -20
spectro(ccex, 
        scale = F, grid = F, 
        flim = c(0,5), tlim = c(0.4, 1.8),
        collevels = seq(-30, 0, by = 0.1),
        ovlp = 95);
for (i in 1:length(ccex.s)) {
  segments(y0 = CCMaxFreq(x = ccex, y = ccex.s)[i],
        y = CCMaxFreq(x = ccex, y = ccex.s)[i],
        x0 = ccex.s$s.start[i], 
        x = ccex.s$s.end[i]
        )
  segments(y0 = CCMinFreq(x = ccex, y = ccex.s)[i],
        y = CCMinFreq(x = ccex, y = ccex.s)[i],
        x0 = ccex.s$s.start[i], 
        x = ccex.s$s.end[i]
        )
  segments(y0 = CCPeakFreq(x = ccex, y = ccex.s)[i],
        y = CCPeakFreq(x = ccex, y = ccex.s)[i],
        x0 = ccex.s$s.start[i], 
        x = ccex.s$s.end[i]
        )
}





```